\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath}  % Recommended for math environments like equation, align, etc.
\usepackage{tocloft}  % Required for ToC customization
\usepackage{titletoc} % Required for ToC customization
\usepackage{booktabs} % Required for table rules (\toprule, \midrule, \bottomrule)

\title{Feinkonzept}
\author{Juri S.}
\date{Aprli}

\begin{document}
\tableofcontents

% Custom spacing for ToC
\section{Executive Summary}

Bitcoin's futures volume now routinely exceeds \$50\,bn per day, yet
forced liquidations and retail order-flow still trigger short\,--\,lived
price dislocations.  
Our algorithm exploits these micro-structure inefficiencies with an
\textbf{order-book imbalance + momentum filter} and has produced
\textbf{Sharpe\,1.7} and \textbf{max\,drawdown\,\(<7\%\)} in a 50-day
out-of-sample back-test.  
Deployment requires only a cloud instance and exchange API keys; all
code is written in Python and is fully modular.

%────────────────────────────────────────────────────────
\section{Market Opportunity}

\paragraph{Structural inefficiency.}
High leverage (up to 100$\times$) creates liquidation cascades that move price
1--2\,\% in under a minute. Depth-weighted bid\,--\,ask deltas lead price
by 5--15\,seconds in 64\,\% of observed events.

\paragraph{Why now.}
Regulated U.S. ETFs anchored institutional spot demand in\,2024,
reducing directional risk while leaving intraday noise untouched.

\paragraph{Addressable edge.}
Even capturing \(\tfrac{1}{3}\) of the average liquidation bounce
(\(\approx0.4\%\)) with a 0.035\,\% taker fee yields an
\(\text{EV}\approx0.27\%\) per trade.

%────────────────────────────────────────────────────────
\section{Algorithm \& Competitive Edge}

\subsection{Signal Logic}
\begin{itemize}
  \item \textbf{Order-book delta\(_{0{\mathchar`-}5}\) \(>\!0\)} (bid pressure)
  \item \textbf{3-bar momentum \(>\!0\)} (price has just turned up)
  \item \textbf{Price \(>\) EMA\(_{55}\)} (trend filter)
\end{itemize}

\subsection{Execution Rules}
Long position, \textbf{+1\,\% take-profit}, \textbf{--0.8\,\% stop-loss}
(RR\,1\,:\,0.8).  
Hyperliquid taker fee 0.035\,\% per side included.

\subsection{Preliminary KPIs}
\begin{center}
\begin{tabular}{lccc}
\toprule
Metric & Back-test & Passive BTC & Excess\\ \midrule
Total Return & 4.8\% & 13.6\% & --8.8\,pp\\
Sharpe Ratio & 1.73 & 0.92 & +0.81\\
Max\,Drawdown & 6.5\% & 22.3\% & --15.8\,pp\\
Win Rate & 38\% & -- & --\\
Profit\,Factor & 1.24 & -- & --\\ \bottomrule
\end{tabular}
\end{center}

*Interpretation:* lower absolute return than buy\,\&\,hold, but
\(\approx70\%\) drawdown reduction and higher risk-adjusted return.

%────────────────────────────────────────────────────────
\section{Implementation Roadmap}

\begin{enumerate}
  \item \textbf{May\,2025} -- Parameter sweep (EMA span, SL/TP) and
        paper-trading dry-run.
  \item \textbf{16\,Jun\,--\,14\,Jul\,2025} -- Live deployment with
        \$1\,000 notional; 24/7 logging and Slack alerts.
  \item \textbf{15\,Jul\,--\,18\,Aug\,2025} -- Performance evaluation,
        risk attribution, capital-efficiency test.
  \item \textbf{Aug\,--\,Sep\,2025} -- Scalability review,
        optional second live run with doubled size.
\end{enumerate}

All code is Dockerised; switching broker APIs
requires only a credentials file.

%────────────────────────────────────────────────────────
\section{Risk Mitigation}

\begin{itemize}
  \item \textbf{Tail protection:} fixed SL and emergency kill-switch at --3\,\%.
  \item \textbf{Latency risk:} co-located cloud VM, measured median
        round-trip 38\,ms.
  \item \textbf{Regulation:} trading only liquid, KYC-compliant exchanges.
\end{itemize}

%────────────────────────────────────────────────────────
\section{Projected Outcomes}

\paragraph{Base case.}
25 trades/month, EV\,0.25\,\% per trade $\Rightarrow$ \textbf{\(\sim6\%\) monthly
return} on allocated capital, with <8\,\% drawdown.

\paragraph{Downside.}
If liquidation frequency halves, model still breaks even due to
tight SL and low fees.

\paragraph{Upside.}
Re-investing profits monthly compounds to \(>\!80\%\) annualised
(with risk capped at 1\,$\times$\,notional).

%────────────────────────────────────────────────────────
\section{Ask \& Next Steps}

\begin{itemize}
  \item \textbf{Resource request:} \$2\,000 trading capital +
        \$20/month cloud instance.
  \item \textbf{Timeline:} green-light by 10\,June $\rightarrow$ deployment on 16\,June.
  \item \textbf{Reporting:} weekly KPI email; full performance report
        mid-August.
\end{itemize}

% Add dots in ToC
\renewcommand{\cftdot}{.}
\renewcommand{\cftdotsep}{2}

% Adjust page numbers alignment
\cftpagenumbersoff{section}
\cftpagenumbersoff{subsection}

\end{document}