\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\setlist{nosep}
\usepackage{xcolor}
\usepackage{tcolorbox}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{longtable}
\usepackage{pdflscape}
\usepackage{rotating}



\title{Automated Bitcoin Trading – Feinkonzept}
\author{Juri S.}
\date{May 10, 2025}

\begin{document}
\maketitle
\tableofcontents
\newpage

\section{Research Objectives}
\begin{enumerate}
  \item Identify statistically significant signals that indicate potential short-term price moves.
  \item Convert the most promising signal(s) into an executable rule-based strategy.
  \item Evaluate performance via back-testing and a four-week live test (16~Jun – 14~Jul 2025).
  \item Document robustness, limitations and possible improvements.
\end{enumerate}

\section{Contents of Thesis}
\subsection{Market Mechanics}
I briefly outline what Bitcoin is and what the value of Bitcoin represents. How Bitcoin works as a digital currency and why specifically I chose Bitcoin as my trading instrument.


\subsection{From data analysis to trading strategy}
I start by visualizing the data using simple line charts and scatter plots to identify intuitive patterns that appear statistically relevant.
These patterns are then tested for statistical significance using basic methods such as conditional probability comparisons and hypothesis testing, implemented in Python.
I plan to use several indicators and combine them into a trading strategy. 
Different strategies with various indicator combinations will be evaluated using backtesting on historical data and walk-forward analysis.


%Hidden note ------------------------------------------------------------

%out of sample => Data not used for optimization
%in sample => Data used for optimization
¨%As new data come in, we keep optimizing for the best parameters and update the strategy continuously.



\vspace{0.5em}
\noindent\textit{\footnotesize%
\textbf{Indicator} is a statistical measure for current market conditions.
}







\subsection{Risk \& Position Size}
I manage risk by determining trade sizes and setting clear price levels for when to exit trades, both for protecting against losses and taking profits. 

\vspace{0.5em}
\noindent\textit{\footnotesize%
\textbf{stop-loss} Is an order to sell a position if the price drops below a certain level which marks the invalidation of your initial ideas of the trade.
\textbf{Take-profit} Is an order to sell a position if the price rises above a certain level which marks the end of the trade.
}




\newpage

\subsection{Automation and Test Run}


I automate the process of calculating live signals and executing trades on the exchange. The algorithmic trading system will be written in Python and will be run on a PaaS, and includes monitoring for trades and errors with automated alerts. Finally, I run a test phase (paper trading) to make sure everything works as expected before using real money.

\vspace{0.5em}
\noindent\textit{\footnotesize%
\textbf{PaaS} is a cloud platform as a service. It is a platform that allows you to run your own software in the cloud remotely.}


\section*{3\hspace{1em}Project Timeline}
\addcontentsline{toc}{section}{3\hspace{1em}Project Timeline}
\vspace{-0.5em}
\noindent\rule{\textwidth}{0.5pt}

\begin{tabular}{|>{\raggedright\arraybackslash}p{7cm}|>{\raggedright\arraybackslash}p{7cm}|}
\hline
\textbf{Phase} & \textbf{Weeks / Dates}\\ \hline
Exploratory analysis \& signal ideation & KW~17 -- KW~21 (24~Apr -- 26~May)\\ \hline
Parameter tuning \& dry-run (paper trading) & KW~22 -- KW~25 (27~May -- 23~Jun)\\ \hline
Live deployment (real funds) & KW~28 -- KW~31 (8~Jul -- 4~Aug)\\ \hline
Result analysis \& thesis writing & KW~32 (5~Aug -- 11~Aug)\\ \hline
Editing, final layout, submission & KW~33 -- KW~35 (12~Aug -- 1~Sep)\\ \hline
\end{tabular}

\vspace{0.5em}

\begin{tcolorbox}[colback=blue!10!white, colframe=blue!10!white, boxrule=0pt, arc=0pt, left=0pt, right=0pt, top=0pt, bottom=0pt]
\textit{This timeline could change and is just a rough estimate.}
\end{tcolorbox}

\section{Expected Delivery}
\begin{itemize}
  \item Python code for data handling, back-testing and live execution in a GitHub repository.
  \item Example datasets already available at
        \href{https://github.com/AJslashTracey/OBDeltaData}{GitHub repository}.
  \item A statistical report comparing other strategies I tested and other signals I considered.
  \item Final thesis detailing methodology, live results and critical reflection.
\end{itemize}

\end{document}
